---
title: "OddDiceprobability"
author: "teacher"
date: "June 22, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Three games with dice

This is an Challenging game where you are to compute the probability of rolling a given number obtained by summing the numbers on a roll of dice. 

### Game one  

Each die has 6 sides (it is a cube) however the distribution of the numbers on the dice is not uniform.  

die number one has these 6 numbers  0,1,2,2,3,4  
die number two has 1,1,2,3,3,4  
die number three has 1,1,1,2,3,4  

It should be easy to see that any number from 2 to 12 is a possibility.  

Determine the probability of rolling a seven?

### Game two

you have two standard dice  
both have 6 sides 

Determine the probability of rolling a seven?  

### Game three  

You have three dice.Each die has four sides (they look like little pyramids).
They each have the numbers 1,2,3, and 4 on their respective faces. When you roll them it is the number that is face down that you count.  In this setup the possible outcomes are the numbers from 3 throughn 12.  
Determine the probability of rolling a seven? 

We will approach this by creating a situation that models the setting as described. We will model each die as an array containing the numbers 1 thru 4. We will call them die_1 , thru die_3. Then we simulate rolling the dies by using the R function "sample". Each time we "roll" the three dice we add them together and put the result into the next open element into the array we called "count". When that is finished the table command applied to the array count summarises our results.

```{r}
die_1=c(1:4)
die_2=c(1:4)
die_3=c(1:4)
count=numeric()
for(i in 1:10000){
  s1=sample(die_1,size=1)
  s2=sample(die_2,size=1)
  s3=sample(die_3,size=1)
  count[i] = sum(s1,s2,s3)
}
table(count)

```


### Final Summary

List in decreasing order the probability of rolling a seven and what you determined those probabilities to be.